---
title: 'Urban Ecosystems (UECO) TEMPLATE [replace with the paper title]'
author: 'Dexter H. Locke, PhD^a^ [replace with your (co)author name(s)]'
date: '`r format(Sys.time())`'
output: 
     word_document:
          reference_docx: UECO_Template.docx
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo=FALSE, include=FALSE}
# The UECO submission guidelines are found here:
# https://www.springer.com/life+sciences/ecology/journal/11252

# RStudio's "R Markdown Cheat Sheet" can be found here
# https://www.rstudio.com/wp-content/uploads/2015/02/rmarkdown-cheatsheet.pdf

# anther useful reource is this blog post called 
# "Happy collaboration with Rmd to docx", which this workflow is largely based on
# https://rmarkdown.rstudio.com/articles_docx.html

# consider starting the R code here
# maybe just set up the working directory, load the libraries,
# read in the data, clea the data

library(tidyverse)
library(knitr)

# set a significance threshold
SigLevel <- 0.05
```

This document was last Knit on `r Sys.time()`, which is in YYYY-MM-DD HH:MM:SS GMT format.  Note that red text within [ ] are instructions, tips, reminders and/or guides  and intended to be helpful. If they are not, then delete them! :-)

The file path associated with this Knit and project is `r getwd()`  

^a^National Socio-Environmental Synthesis Center (SESYNC)   
1 Park Place  
Annapolis MD 01610-1477  
USA  
PHONE 310 463 6202  
EMAIL dexter.locke@gmail.com, dlocke@sesync.org
http://dexterlocke.com/


# Abstract
[250 words or less]  

Begin typing here  


# Keywords

[3-6]  

Examples: Tree canopy, remote sensing, urban ecology, urban forestry, Latin America and the Caribbean  

# Reserach Highlights

[3-5]  

Examples: Tree canopy, remote sensing, urban ecology, urban forestry, Latin America and the Caribbean  


# 1. Introduction

[This section describes the motivation for the research question in two pages  
give the reader:  
hook  
problem  
purpose  
allude to methods  
set up the research questions]  


# 2. Method
## 2.1 Study Area
[This section describes the study area in a few paragraphs, and preferably why this is ‘good’ area for these questions]  

Begin typing here  


## 2.2 Data
[What data were used, why are they well-matched the research questions and relevant. Citations and/or links to (OPEN?) data sources should be provided]  

Begin typing here  


## 2.3. Analysis
### 2.3.1 Subsection 1?
[This section describes the data preparation such as making derivative products from the inputs, geoprocessing, or any other similar preparation steps]  

Begin typing here  


### 2.3.1 Subsection 2?:
[if needed]  

Begin typing here 

All statistical analyses were carried out with `r R.version.string`.

We define statistically significant as a p-value of <`r SigLevel`.


# 3. Results
[This section describes the results without interpretation in two pages.]  

## 3.1. Example subsection

## 3.2. Example subsection 2

**(Table 1).** Title of the first table
```{r, echo=FALSE, include=TRUE}
# consider starting the R code here, If yo haven't already above
# maybe just set up the working directory, load the libraries,
# read in the data, clea the data


```

# 4. Discussion
[Justification and main finding]

Begin typing here 


# 5. Conclusions
[This section gives the most important message in less than one page.]  

Begin typing here  

# Acknowledgements
[Grants, etc. Anonymous reviewers supplied constructive feedback that helped to improve this paper. Consider acknowledging this repo! https://github.com/DHLocke/R_Markdown_Journal_Templates]  

This work was supported by the National Socio-Environmental Synthesis Center (SESYNC) under funding received from the National Science Foundation DBI-1639145.

# References
[Citation
Cite references in the text by name and year in parentheses. Some examples:
Negotiation research spans many disciplines (Thompson 1990).
This result was later contradicted by Becker and Seligman (1996).
This effect has been widely studied (Abbott 1991; Barakat et al. 1995a, b; Kelso and Smith 1998; Medvec et al. 1999, 2000).
Reference list
The list of references should only include works that are cited in the text and that have been published or accepted for publication. Personal communications and unpublished works should only be mentioned in the text. Do not use footnotes or endnotes as a substitute for a reference list.
Reference list entries should be alphabetized by the last names of the first author of each work. Order multi-author publications of the same first author alphabetically with respect to second, third, etc. author. Publications of exactly the same author(s) must be ordered chronologically.
Journal article
Gamelin FX, Baquet G, Berthoin S, Thevenet D, Nourry C, Nottin S, Bosquet L (2009) Effect of high intensity intermittent training on heart rate variability in prepubescent children. Eur J Appl Physiol 105:731-738. https://doi.org/10.1007/s00421-008-0955-8
Ideally, the names of all authors should be provided, but the usage of “et al” in long author lists will also be accepted:
Smith J, Jones M Jr, Houghton L et al (1999) Future of health insurance. N Engl J Med 965:325–329
Article by DOI
Slifka MK, Whitton JL (2000) Clinical implications of dysregulated cytokine production. J Mol Med. https://doi.org/10.1007/s001090000086
Book
South J, Blass B (2001) The future of modern genomics. Blackwell, London
Book chapter
Brown B, Aaron M (2001) The politics of nature. In: Smith J (ed) The rise of modern genomics, 3rd edn. Wiley, New York, pp 230-257
Online document
Cartwright J (2007) Big stars have weather too. IOP Publishing PhysicsWeb. http://physicsweb.org/articles/news/11/6/16/1. Accessed 26 June 2007
Dissertation
Trent JW (1975) Experimental acute renal failure. Dissertation, University of California
Always use the standard abbreviation of a journal’s name according to the ISSN List of Title Word Abbreviations, see
ISSN LTWA
If you are unsure, please use the full journal title.
For authors using EndNote, Springer provides an output style that supports the formatting of in-text citations and reference list.
EndNote style (zip, 2 kB)]

Begin typing here  


# Figures (if not alredy Knit into the text)

# Tables (if not alredy Knit into the text)

# Appendix
[The appendix gives technical material that is important but too long and detailed for most readers. Most papers will not have an appendix.  Consider also including links to data and reproducible R code]


```{r, include=TRUE}
sessionInfo()
# End on
date()
```