---
title: 'Landscape and Urban Planning (LAUP) TEMPLATE [replace with the paper title]'
author: 'Dexter H. Locke, PhD^a^ [replace with your (co)author name(s)]'
date: '`r format(Sys.time())`'
output: 
     word_document:
          reference_docx: LAUP_Template.docx
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo=FALSE, include=FALSE}
# The LAUP submission guidelines are found here:
# https://www.elsevier.com/journals/landscape-and-urban-planning/0169-2046?generatepdf=true

# RStudio's "R Markdown Cheat Sheet" can be found here
# https://www.rstudio.com/wp-content/uploads/2015/02/rmarkdown-cheatsheet.pdf

# anther useful reource is this blog post called 
# "Happy collaboration with Rmd to docx", which this workflow is largely based on
# https://rmarkdown.rstudio.com/articles_docx.html

# consider starting the R code here
# maybe just set up the working directory, load the libraries,
# read in the data, clea the data

library(tidyverse)
library(knitr)

# set a significance threshold
SigLevel <- 0.05
```

This document was last Knit on `r Sys.time()`, which is in YYYY-MM-DD HH:MM:SS GMT format.  Note that red text within [ ] are instructions, tips, reminders and/or guides  and intended to be helpful. If they are not, then delete them! :-)

The file path associated with this Knit and project is `r getwd()`  

^a^National Socio-Environmental Synthesis Center (SESYNC)   
1 Park Place  
Annapolis MD 01610-1477  
USA  
PHONE 310 463 6202  
EMAIL dexter.locke@gmail.com, dlocke@sesync.org
http://dexterlocke.com/


# Abstract
[250 words or less]  

Begin typing here  


# Keywords

[3-6]  

Examples: Tree canopy, remote sensing, urban ecology, urban forestry, Latin America and the Caribbean  

# Reserach Highlights

[3-5]  

Examples: Tree canopy, remote sensing, urban ecology, urban forestry, Latin America and the Caribbean  


# 1. Introduction

[This section describes the motivation for the research question in two pages  
give the reader:  
hook  
problem  
purpose  
allude to methods  
set up the research questions]  


# 2. Method
## 2.1 Study Area
[This section describes the study area in a few paragraphs, and preferably why this is ‘good’ area for these questions]  

Begin typing here  


## 2.2 Data
[What data were used, why are they well-matched the research questions and relevant. Citations and/or links to (OPEN?) data sources should be provided]  

Begin typing here  


## 2.3. Analysis
### 2.3.1 Subsection 1?
[This section describes the data preparation such as making derivative products from the inputs, geoprocessing, or any other similar preparation steps]  

Begin typing here  


### 2.3.1 Subsection 2?:
[if needed]  

Begin typing here 

All statistical analyses were carried out with `r R.version.string`.

We define statistically significant as a p-value of <`r SigLevel`.


# 3. Results
[This section describes the results without interpretation in two pages.]  

## 3.1. Example subsection

## 3.2. Example subsection 2

**(Table 1).** Title of the first table
```{r, echo=FALSE, include=TRUE}
# consider starting the R code here, If yo haven't already above
# maybe just set up the working directory, load the libraries,
# read in the data, clea the data


```

# 4. Discussion
[Justification and main finding]

Begin typing here 


# 5. Conclusions
[This section gives the most important message in less than one page.]  

Begin typing here  

# Acknowledgements
[Grants, etc. Anonymous reviewers supplied constructive feedback that helped to improve this paper.]  

This work was supported by the National Socio-Environmental Synthesis Center (SESYNC) under funding received from the National Science Foundation DBI-1639145.

# References
[References - Assertions made in the paper that are not supported solely by your research and rely in
part or whole on work by others must appropriately referenced. Emphasize scholarly, peer-reviewed
publications that are internationally accessible. Follow the APA 6th ed. format for all source types in
the reference list and in-text citations (see basic examples below). Ensure that all references cited
in the text are also in the reference list (and vice versa). References and multiple in-text citations
should be arranged first alphabetically and, if necessary, further sorted chronologically. More than
one reference from the same author(s) in the same year should be identified by the letters "a", "b",
"c", etc., placed after the year of publication. Special cases include:
Digital object identifier (DOI) - The digital object identifier (DOI) provides a persistent link to
electronically available journal articles and some other sources. It should be included at the end of
a reference when available (see example below). Uniform resource locators (URL) - References
to published and unpublished documents, websites, and other sources that are primarily accessed
through the Internet should include the URL after providing regular citation information in as complete
a form as possible (see examples below). Include the retrieval date only if the source material linked
to the URL changes over time. Accepted and in press publications - References to sources that
have been recently accepted for publication or are already in press should be cited using as complete
of information as possible, including volume/issue numbers and DOI/URLs. Authors should make
every attempt to update such references as papers move through revision to acceptance and page
proofs. Work in preparation, submitted, under review, etc. - Work destined for publication that
has not yet been officially accepted should not be listed in the reference list. Limited citation of such
work may be included in the body of the text only, and should be referred to as unpublished data, for
example: (Gobster and Xiang, unpublished data). Non-refereed works - References to unpublished
and/or non-refereed sources such as unpublished data, newspaper and popular magazine articles,
websites, and other "gray literature" should be used sparingly and not to support claims made in the
paper. Exceptions to this include unpublished theses and dissertations. Personal communications
- Interviews, private e-mails and letters, and other personal communications are not considered
recoverable data and thus should not be included in your reference list. If included in your work,
they should be referenced within the text by name and date of the communication, e.g. - A. Smith
(personal communication, January 10, 2012), (A. Smith, personal communication, January 10, 2012).
Non-English references - Non-English references should be used sparingly and in cases where the
source provides essential support to your work and more widely accessible English language sources
cannot substitute. Provide an English translation after the original title (see example 6 below)
Basic reference list examples -
Journal article - Hersperger, A. M., Langhamer, D., & Dalang, T. (2012). Inventorying humanmade objects - A step towards better understanding land use for multifunctional planning in
a periurban Swiss landscape. Landscape and Urban Planning, 105(3), 307-314. doi - 10.1016/
j.landurbplan.2012.01.008 Book - Niemela, J. (Ed.). (2012). Urban ecology - Patterns, processes
and applications. New York - Oxford. Chapter in an edited book - McDonnell, M. J., & Hahs, A.
K. (2009). Comparative ecology of cities and towns - Past, present and future. In M. J. McDonnell,
A. K. Hahs, & J. H. Breuste (Eds.), Ecology of cities and towns - A comparative approach (pp.
71-89). New York - Cambridge. Technical or research report, published in print and online
 - Gobster, P. H., and & Haight, R. G. (2004). From landscapes to lots - Understanding and
managing Midwestern landscape change (General Technical Report NC-245). St. Paul, MN - U.S.
Department of Agriculture, Forest Service, North Central Research Station. Retrieved from - http
-//www.nrs.fs.fed.us/pubs/gtr/gtr_nc245.pdf Web pages and other online-only sources with
changing content - Editor. (n.d.). Guide for authors. Landscape and Urban Planning, Retrieved
January 1, 2012 from https://www.elsevier.com/journals/landscape-and-urban-planning/0169-2046/
guide-for-authors Journal article, non-English source - Vogel, B., Molich, T., & Klar, N. (2009). Der
Wildkatzenwegeplan - Ein strategisches Instrument des Naturschutz (The Wildcat Infrastructure Plan
- A strategic instrument of nature conservation). Naturschutz und Landschaftsplanung, 41, 333-340.
Basic in-text reference examples - Authors cited outside and within parentheses - "We
used the Cuzick and Edwards (1990) test... ... summed across all cases (Cuzick & Edwards, 1990)".
Multiple works in same parentheses - "...urban areas tended to have less diverse assemblages
of bird species than adjacent natural areas (Beissinger & Osborne, 1982; Cam, Nichols, Sauer, Hines,
& Flather, 2000; Gavareski, 1976)..." Multiple authors, 2nd occurrence - "...responses to habitat
features were scale dependent (Bolger, Scott, & Rotenberry, 1997; Cam et al., 2000)."]

Begin typing here  


# Figures (if not alredy Knit into the text)

# Tables (if not alredy Knit into the text)

# Appendix
[The appendix gives technical material that is important but too long and detailed for most readers. Most papers will not have an appendix.  Consider also including links to data and reproducible R code]


```{r, include=TRUE}
sessionInfo()
# End on
date()
```